\section{Background}\label{sec:background}
This section introduces some formal definitions related to the graph matching problem.

\subsection{Property Graph}
A \emph{property graph} is a directed graph with labeled vertices and edges.
Cycles and multiple edges (parallel arcs with the same source and destination) may also present between a pair of vertices.

\begin{definition}[Property Graph~\cite{DBLP:journals/csur/AnglesABHRV17}]
  A property graph $G$ is a tuple $(V, E, \rho, \lambda, \sigma)$, where:
  \begin{enumerate}[noitemsep,label={(\arabic*)}]
  \item $V$ is a finite set of vertices.
  \item $E$ is a finite set of edges.
  \item $\rho: E \rightarrow (V \times V)$ is a total function.
    Intuitively, $\rho(e) = (v_1, v_2)$ indicates that $e$ is a directed edge from $v_1$ to $v_2$.
  \item $\lambda: (V \cup E) \rightarrow L$ is a total function where $L$ is a set of labels.
    Intuitively, if $v \in V, \rho(v) = l$ (respectively, $e \in E, \rho(e) = l$),
    $l$ is the label of vertex $v$ (respectively, edge $e$).
  \item $\sigma: (V \cup E) \times Prop \rightarrow Val$ is a partial function assigning values for properties to vertices/edges.
  \end{enumerate}
\end{definition}

Formally, a property graph $G$ can be denoted as a 5-tuple $(V(G), E(G), \rho_G, \lambda_G, \sigma_G)$.
Under the property graph model, each vertex/edge has a single label representing the type of the entity/relationship.
Key-value pairs are associated with vertices and edges to represent the attributes, e.g., every vertex has a ID property storing an integer as the identifier of the vertex.
The property graph model is widely adopted by major industrial graph databases, such as Neo4j~\cite{Neo4j}.

\begin{definition}[Vertex Cover]
  For a property graph $G$ = ($V(G)$, $E(G)$, $\rho_G$, $\lambda_G$), a set $V_c$ ($V_c \subseteq V(G)$) is a vertex cover of $G$
  if $\forall e \in E(G)$, $V_c \cap \{ v_1, v_2 \} \ne \emptyset$, where $(v_1, v_2) = \rho_G(e)$.
\end{definition}
A vertex cover $V_c$ of $G$ is a subset of $V(G)$ such that every edge of $G$ has at least one member of $V_c$ as an endpoint.

\subsection{Property Graph Matching Problem}
\begin{definition}[Subgraph]
  A property graph $H$ is called a subgraph of a property graph $G$, denoted as $H \subseteq G$, if
  $V(H) \subseteq V(G)$, $E(H) \subseteq E(G)$, $\rho_H$ is a restriction of $\rho_G$, and $\lambda_H$ is a restriction of $\lambda_G$.
\end{definition}
Note that the restriction means the subgraph $H$ must contain all edges in $G$ connecting all vertices in $H$.

\begin{definition}[Property Graph Isomorphism]
  Two property graphs $G$ and $H$ are isomorphic, denoted as $G \cong H$,
  if there exists bijections $\theta: V(G) \rightarrow V(H)$ and $\phi: E(G) \rightarrow E(H)$ such that
  $\rho_G(e) = (u, v)$ if and only if $\rho_H(\phi(e)) = (\theta(u), \theta(v))$,
  $\lambda_G(v) = \lambda_H(\theta(v))$ for all $v \in V(G)$
  and $\lambda_G(e) = \lambda_H(\phi(e))$ for all $e \in E(G)$;
  Such a pair of mappings is called an isomorphism between $G$ and $H$.
\end{definition}
The property graph isomorphism problem is to find all subgraphs of the data graph that are isomorphic to the pattern.
Unlike the simple graph model, the property graph isomorphism problem is much more complicated.
As the vertices and edges are labeled in a property graph, we need to check  not only the topological structure,
but also the labels to determine whether two property graphs are isomorphic.
And the existence of multi-edge connecting two vertices makes it even harder to check the isomorphism.
\begin{definition}[Property Graph Matching]\label{def:property_graph_matching}
  Given a data property graph $D$, a pattern property graph $P$ and a searching condition $\psi: \mathcal{G} \rightarrow \mathcal{B}$ with $\mathcal{G}$ the set of property graphs and $\mathcal{B}$ the set of Boolean values,
  the property graph matching problem is to report the set $\mathcal{I} = \{H | H \subseteq D, H \cong P, \psi(H) = true\}$.
\end{definition}
The property graph matching problem extends the property graph isomorphism problem by introducing the searching conditions (WHERE clauses).
Existing works usually omit the searching condition $\psi$ in their definition of graph matching~\cite{DBLP:conf/sigmod/ShaoCCMYX14,DBLP:journals/pvldb/LaiQLC15,DBLP:conf/sigmod/KimLBHLKJ16,DBLP:journals/pvldb/QiaoZC17}.
And they adopt a related technique called \emph{symmetry-breaking}~\cite{DBLP:conf/recomb/GrochowK07},
which can be viewed as a \emph{special} case of WHERE clause by providing a partial order on $V(P)$ after exploiting the automorphism of $P$.
However, the WHERE clause is \emph{general}. Users of real-world graph databases usually provide their self-defined searching condition $\psi$ to filter out unnecessary matching, not only symmetry-breaking conditions.
