% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm]{acmart}

\usepackage{amsmath}
\newtheorem{definition}{Definition}
\usepackage{fancyvrb}
\usepackage{bbding}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{balance}
\usepackage{hyperref}
\usepackage[inline]{enumitem}
\usepackage[linesnumbered,ruled,noend]{algorithm2e}
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\SetKwProg{Fn}{function}{}{end}
\SetKwSwitch{Match}{Case}{Other}{match}{do}{case}{otherwise}{endcase}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{14}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2021}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle}
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{http://vldb.org/pvldb/format_vol14.html}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain}

\begin{document}
\title{SeqStar: A Fast Out-of-Core Property Graph Matching System}

%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
\author{Yanxuan Cui}
\affiliation{%
  \institution{Tsinghua University}
  \city{Being}
  \state{China}
}
\email{cuiyx18@mails.tsinghua.edu.cn}

\author{Kang Chen}
\affiliation{%
  \institution{Tsinghua University}
  \city{Being}
  \state{China}
}
\email{chenkang@tsinghua.edu.cn}

\author{Mingxing Zhang}
\affiliation{%
  \institution{Tsinghua University}
  \city{Being}
  \state{China}
}
\affiliation{%
  \institution{Sangfor Technologies Inc.}
  \city{Shenzhen}
  \state{China}
}
\email{zhang.mingxing@outlook.com}

\author{Zhiyuan Ma}
\affiliation{%
  \institution{Tsinghua University}
  \city{Being}
  \state{China}
}
\email{mazy19@mails.tsinghua.edu.cn}

\author{Juan Yang}
\affiliation{%
  \institution{Beijing HaiZhi XingTu Technology Co., Ltd.}
  \city{Being}
  \state{China}
}
\email{yangjuan@stargraph.cn}

\author{Yongwei Wu}
\affiliation{%
  \institution{Tsinghua University}
  \city{Being}
  \state{China}
}
\email{wuyw@tsinghua.edu.cn}

\input{sections/abstract}

\maketitle

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\pagestyle{\vldbpagestyle}
\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\endgroup
\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author\@(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright{} Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150--8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\ifdefempty{\vldbavailabilityurl}{}{
\vspace{.3cm}
\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
\endgroup
}
%%% VLDB block end %%%
\input{sections/introduction}
\input{sections/background}
\input{sections/framework}
\input{sections/storage}
\input{sections/match}
\input{sections/experiments}
\input{sections/related_work}
\input{sections/conclusion}

%\clearpage
\balance{}
\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}

\end{document}
\endinput
