\begin{abstract}
  Property graph matching is one of the most important operations of graph databases and has a wide range of applications.
  The problem has been studied extensively, however, on simplified graph models.
  Because of the complexity involving directions, multi-edges, labels in real-world property graphs,
  optimizations aimed at simple graphs are not suitable to handle the storage and matching challenges of property graphs.
  Moreover, existing approaches rely on huge memory resources to run their system which hinders the adoption of the graph matching technology.
  %popularity of graph technology.

  We present SeqStar, a fast out-of-core property graph matching system that can execute real-world complex queries efficiently.
  %% We present SeqStar, the first out-of-core property graph matching system that can execute real-world complex queries efficiently.
  The storage engine of SeqStar uses a novel \emph{vertex-centric} storage model.
  By storing necessary information associated with one vertex together,
  SeqStar avoids the random disk access problem in existing works.
  In the graph matching engine, we propose a novel star decomposition algorithm that preserves all the relevant filtering information on stars.
  Therefore, SeqStar can filter out more unnecessary matchings in the early matching stages.
  To reduce the memory usage, SeqStar compresses the intermediate results from star matching by postponing Cartesian product and combining equivalent vertices.
  The WHERE clause is better supported by the predicate pushdown method for SeqStar to optimize real-world queries.
  Extensive experiments show the superior performance of SeqStar over existing systems.
  SeqStar is able to run complex real-world queries that are not runnable in existing systems.
\end{abstract}
